Usage metrics

### 2020-12-16 analysis/usage.Rmd
minor

```{r triggered-sites, include=F}
stopifnot(sum(is.na(E$src_ref)) == 0) # No NAs in scr_ref!

sites <- E %>% # src_ref indicates where the call originates from.
  pull(src_ref) %>%
  n_distinct() # This the number of distinct sites

sites_per_package <- E %>%
  count(ev_package, src_ref) %>%
  count(ev_package) # All packages have at least one site!

max_packages <- sites_per_package %>%
  filter(n == max(n)) %>%
  .$n

TBL <- overview_table(
  # Sites triggered over the whole corpus:
  r("nb eval call sites", sites),
  # How many packages in the corpus have a single triggered call site:
  r("nb one call site", sites_per_package %>% filter(n == 1)),
  r("at least one call site", nrow(sites_per_package)),
  r("packages no calls to eval", corpus_size - nrow(sites_per_package)),
  r("nb median call sites", median(sites_per_package$n)),
  r("max call sites", max_packages),
)
```

@@

```{r call-sites-violin-plot, include=F}
E %>%
  group_by(ev_package) %>%
  mutate(sites = n_distinct(src_ref)) %>%
  ggplot(aes(x = ev_variant, y = sites, fill = ev_variant), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  # geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y = "Call sites per package") +
  theme(
    legend.position = c(0.5, 0.85),
    legend.box.background = element_rect(fill = "white", size = 0.1),
    legend.box = "horizontal",
    axis.title.x = element_blank()
  ) -> PLOT

ggsave(path(PLOT_DIR, "call_sites_per_packages.pdf"))
```

@@

```{r nb-eval-calls}
# run = package?

### TODO REMOVE
eval_calls_per_package <- E %>%
  count(ev_package, wt = duplicates) %>%
  left_join(runs_package, by = "ev_package")

average_eval_calls <- eval_calls_per_package %>%
  filter(n > 0) %>%
  summarise(average = mean(n))
max_eval_calls <- eval_calls_per_package %>% filter(n == max(n))

r("average eval calls per package", average_eval_calls$average) # average on packages with at least one eval call
r("max eval calls", max_eval_calls$n)
r("max eval call package", max_eval_calls$ev_package)
```

>>>>

```{r triggered-sites, include=F}
stopifnot(sum(is.na(E$src_ref)) == 0) # No NAs in scr_ref!
# Number of eval call sites
sites <- E %>% # src_ref indicates where the call originates from.
  pull(src_ref) %>%
  n_distinct() # This the number of distinct sites
# Number of call sites per package
sites_per_package <- E %>%
  count(ev_package, src_ref) %>%
  count(ev_package) # All packages have at least one site!

TBL <- overview_table(
  # Sites triggered over the whole corpus:
  r("nb eval call sites", sites),
  # How many packages in the corpus have a single triggered call site:
  r("nb one call site", sites_per_package %>% filter(n == 1)),
  r("at least one call site", nrow(sites_per_package)),
  r("packages no calls to eval", corpus_size - nrow(sites_per_package)),
  r("nb median call sites", median(sites_per_package$n))
)
```

@@

@@
